---
title: "Social Media Setup APIs: Twitter `r icon::fa_twitter(colour='#00aced')`, Facebook `r icon::fa_facebook_f(colour='#3B5998')` and Instagram `r icon::fa_instagram(colour='#fb3958')`"
author: "**useR! 2018**"
date: "11th Feb 2018"
output:
  html_document:
    toc: yes
    toc_depth: 3
  github_document:
    toc: yes
    toc_depth: 3
---

```{r include=FALSE,echo=FALSE}
library(knitr)
library(magick)
# Chunk options
knitr::opts_chunk$set(fig.width=7,echo=TRUE, fig.height=7, warning=FALSE, message=FALSE,prompt=T,tidy=T,include=TRUE,cache=TRUE,fig.align='center',fig.asp=0.50,opts.label ="squarefigure",cache = FALSE)

library(png)
library(grid)
# devtools::install_github("hadley/emo")
library(emo)

```

# Twitter 

## Reference material for the following tutorial

* [Setting up the Twitter R package for text analytics](https://www.r-bloggers.com/setting-up-the-twitter-r-package-for-text-analytics/)

## Setup a Twitter account and create an App

1. Setup your `username` and `password` at https://twitter.com/. 
2. Go to https://apps.twitter.com/ and sign in with your `username` and `password`
3. Click on `Create a new App`

```{r CreateAnApp,echo=FALSE,fig.cap="Create a Twitter app at https://apps.twitter.com/."}
img <- readPNG(file.path("Social_Media_Setup_APIs_figures/CreateAnApp.png"))
#grid.raster(img)

img%>%grid.raster()
```

4. Fill in with you App name, brief description and a website. Ideally this website is where people can find more information about your app. However, if you don't have one just insert a valid link to a web page.

5. As `callback URL` set: http://127.0.0.1:1410 

```{r RladiesApp,echo=FALSE,fig.cap="Setup your app information andcallback URL."}
img <- readPNG(file.path("Social_Media_Setup_APIs_figures/RladiesApp.png"))
grid.raster(img)
```

6. Once you click on `Create your Twitter Application` you will be re-directed to your application page. You're almost there! Go to the `Keys and Access Tokens` tab and at the bootom of this page click on `Create my access token`. Your access token will appear at the bottom of the page.

```{r AccessToken,echo=FALSE,fig.width=3, fig.height=3,fig.cap="Create access token to connect R with Twitter."}
img <- readPNG(file.path("Social_Media_Setup_APIs_figures/acessToken.png"))
grid.raster(img)
```


7. Now you have everything you need to connect `R` with Twitter! From your application page you need **four** things:

* API key
* API secret
* Token
* Token secret


```{r key_and_token_example,echo=FALSE,fig.cap="Create access token to connect R with Twitter.",fig.height=15,fig.width=15}
img <- readPNG(file.path("Social_Media_Setup_APIs_figures/key_and_token_example.png"))
grid.raster(img)
```


## Connect your R session with Twitter

There are two well-known packages used to collect data from Twitter directly into R:

* `twitteR` https://cran.r-project.org/web/packages/twitteR/README.html
* `rtweet` https://cran.r-project.org/web/packages/rtweet/index.html

## Setup your R session to download Twitter data with the `twitteR` package

The function `twitteR::searchTwitter` will return a list of tweets which you can easily coherce to standard `data.frame` with the function `twitteR::twListToDF`.

```{r eval=FALSE}
api_key <-'your_api_key'
api_secret<- 'your_api_secret'
token <- 'your_token'
token_secret<- 'your_token_secret'

setup_twitter_oauth(api_key, api_secret, token, token_secret)

# Search tweets
MyTweets <- searchTwitter('#MyChosenHastags',lang="en")
```

## Setup your R session to download Twitter data with the `rtweet` package

**Note**: Remember to set `set_renv=FALSE` when you run the `rtweet::create_token()` function. The default should be set to `FALSE` as mentioned in the help page `?rtweet` but it is instead set to `TRUE`. If `set_renv=TRUE` it will save a hidden token named `.rtweet_token.rds` which will be used as the default evironemnt twietter token variable. 

More information about this can be found at [Obtaining and using access tokens](https://cran.r-project.org/web/packages/rtweet/vignettes/auth.html).

The function `rtweet::search_tweets` returns tweets already as a data frame.

```{r eval=FALSE}
appname <- 'Rladies_app'
api_key <-'your_api_key'
api_secret<- 'your_api_secret'

setup_twitter_oauth(api_key, api_secret, token, token_secret)

## create token named "twitter_token"
twitter_token <- create_token(
  app = appname,
  consumer_key = key,
  consumer_secret = secret)

MyTweet <- search_tweets('#MyChosenHastags',lang="en", token = twitter_token)
```

# YouTube
## Reference material for the following tutorial

* [Setting up Google API for YouTube analytics](https://www.youtube.com/embed/Im69kzhpR3I)

## Setup a Google account and create an App

If you do not have a Google account, you can create one at [Google](https://www.google.com/accounts/NewAccount) 

Go to the [Google Developers Console] (https://console.developers.google.com/) and create a project there

Obtain authorisation credentials

To use YouTube data API you need to have authorization credentials. 
The API supports API keys and OAuth 2.0 credentials. 

The tuber package uses OAuth 2.0, but you will also need the API keys for some data extraction, e.g. obtaining YouTube channel ID. 

To set up your credentials, you go to the Credentials section in your Google Developers Console. 

For the OAuth 2.0 setup, set “Authorized redirect URIs” as  http://localhost:1410/

Note down the following:

* `Your API key:`
* `OAuth 2.0 credentials:`
* `Name:` 
* `Client ID:`
* `Client secret:`

# Facebook

```{r eval=FALSE}
install.packages("devtools")
install_github("pablobarbera/Rfacebook", subdir="Rfacebook")
install.packages("httr")
```


```{r}
library(devtools)
library (Rfacebook)
library(httr)
library(jsonlite)
```

## Option 1: connect via the facebook API

* Need to set up access in the facebook first at https://developers.facebook.com

```{r eval=FALSE}
app_id1<-"useYours"
app_secret1<-"useYous"

fb_oauth <- fbOAuth(app_id=app_id1, app_secret=app_secret1,extended_permissions = FALSE)
```


```{r eval=FALSE}
facebook <- oauth_endpoint(
  authorize = 'https://www.facebook.com/dialog/oauth',
  access = 'https://graph.facebook.com/oauth/access_token')
```

* Credentials you get from registering a new application

* OAuth endpoints given in the Facebook API documentation
  1. authorization_base_url = 'https://www.facebook.com/dialog/oauth'
  2. token_url = 'https://graph.facebook.com/oauth/access_token'
  3. redirect_uri = 'http://localhost:1410/', this should match Site URL

```{r eval=FALSE}
app_name<-"useR2018" #not used but good for organisation
client_id = app_id1
client_secret = app_secret1
  
myapp <- oauth_app(app_name, client_id, client_secret)


facebook_oauth<- oauth2.0_token(facebook, myapp)
save(facebook_oauth, file="fb_oauth")

load("fb_oauth")

token<-facebook_oauth$credentials$access_token

me <- getUsers("me",token=fb_oauth)

me2 <- getUsers("me",token=token)

#getUsers(c("barackobama", "donaldtrump"), token)
#getUsers(c("barackobama", "donaldtrump"), fb_oauth)

```


## Option 2: connect via the authentication token

* Manually created 
* Has less restrictions= more data.
* Valid for 2 hours!!!!!
* Create your token at https://developers.facebook.com/tools/explorer


# Instagram

```{r eval=FALSE}
install.packages("httpuv")
install.packages("httr")
install.packages("jsonlite")
install.packages("RCurl")
```

```{r eval=FALSE}
require(httr) 
require(jsonlite)
require(RCurl)
```

```{r eval=FALSE}

full_url <- oauth_callback()
full_url <- gsub("(.*localhost:[0-9]{1,5}/).*", x=full_url, replacement="\\1")
print(full_url)

#http://localhost:1410/

#register your client in Instagram
#Parameters to use
  
#define 4 variables
#get the first 3 from the instagram setup  
app_name <- "useYour"
client_id <- "useYour"
client_secret <- "useYour"

#set the type of access
scope = "public_content"
  
#set access points for authorization
#https://www.instagram.com/developer/endpoints/users/
instagram <- oauth_endpoint(
  authorize = "https://api.instagram.com/oauth/authorize",
  access = "https://api.instagram.com/oauth/access_token")

#the application that will be used to access Ig
myapp <- oauth_app(app_name, client_id, client_secret)

#authentication

#ig_oauth <- oauth2.0_token(instagram, myapp,scope="basic",  type = "application/x-www-form-urlencoded",cache=FALSE)

ig_oauth <- oauth2.0_token(instagram, myapp,scope="basic")


save(ig_oauth, file="ig_oauth")
load("ig_oauth")

token<-ig_oauth$credentials$access_token

```

