---
title: "Social Media Setup APIs: Twitter `r icon::fa_twitter(colour='#00aced')`, Facebook `r icon::fa_facebook_f(colour='#3B5998')` and Instagram `r icon::fa_instagram(colour='#fb3958')`"
author: "**useR! 2018**"
date: "11th Feb 2018"
output:
  html_document:
    toc: yes
    toc_depth: 3
  github_document:
    toc: yes
    toc_depth: 3
---

```{r include=FALSE,echo=FALSE}
library(knitr)
library(magick)
# Chunk options
knitr::opts_chunk$set(fig.width=7,echo=TRUE, fig.height=7, warning=FALSE, message=FALSE,prompt=T,tidy=T,include=TRUE,cache=TRUE,fig.align='center',fig.asp=0.50,opts.label ="squarefigure",cache = TRUE)

library(png)
library(grid)
# devtools::install_github("hadley/emo")
library(emo)

```

# Twitter 

## Reference material for the following tutorial

* [Setting up the Twitter R package for text analytics](https://www.r-bloggers.com/setting-up-the-twitter-r-package-for-text-analytics/)

## Setup a Twitter account and create an App

1. Setup your `username` and `password` at https://twitter.com/. 
2. Go to https://apps.twitter.com/ and sign in with your `username` and `password`
3. Click on `Create a new App`

```{r CreateAnApp,echo=FALSE,fig.cap="Create a Twitter app at https://apps.twitter.com/."}
img <- readPNG(file.path("TwitteR_tutorial_data/Figures/CreateAnApp.png"))
#grid.raster(img)

img%>%grid.raster()
```

4. Fill in with you App name, brief description and a website. Ideally this website is where people can find more information about your app. However, if you don't have one just insert a valid link to a web page.

5. As `callback URL` set: http://127.0.0.1:1410 

```{r RladiesApp,echo=FALSE,fig.cap="Setup your app information andcallback URL."}
img <- readPNG(file.path("TwitteR_tutorial_data/Figures/RladiesApp.png"))
grid.raster(img)
```

6. Once you click on `Create your Twitter Application` you will be re-directed to your application page. You're almost there! Go to the `Keys and Access Tokens` tab and at the bootom of this page click on `Create my access token`. Your access token will appear at the bottom of the page.

```{r AccessToken,echo=FALSE,fig.width=3, fig.height=3,fig.cap="Create access token to connect R with Twitter."}
img <- readPNG(file.path("TwitteR_tutorial_data/Figures/acessToken.png"))
grid.raster(img)
```


7. Now you have everything you need to connect `R` with Twitter! From your application page you need **four** things:

* API key
* API secret
* Token
* Token secret


```{r key_and_token_example,echo=FALSE,fig.cap="Create access token to connect R with Twitter.",fig.height=15,fig.width=15}
img <- readPNG(file.path("TwitteR_tutorial_data/Figures/key_and_token_example.png"))
grid.raster(img)
```


## Connect your R session with Twitter

There are two well-known packages used to collect data from Twitter directly into R:

* `twitteR` https://cran.r-project.org/web/packages/twitteR/README.html
* `rtweet` https://cran.r-project.org/web/packages/rtweet/index.html

## Setup your R session to download Twitter data with the `twitteR` package

The function `twitteR::searchTwitter` will return a list of tweets which you can easily coherce to standard `data.frame` with the function `twitteR::twListToDF`.

```{r eval=FALSE}
api_key <-'your_api_key'
api_secret<- 'your_api_secret'
token <- 'your_token'
token_secret<- 'your_token_secret'

setup_twitter_oauth(api_key, api_secret, token, token_secret)

# Search tweets
MyTweets <- searchTwitter('#MyChosenHastags',lang="en")
```

## Setup your R session to download Twitter data with the `rtweet` package

**Note**: Remember to set `set_renv=FALSE` when you run the `rtweet::create_token()` function. The default should be set to `FALSE` as mentioned in the help page `?rtweet` but it is instead set to `TRUE`. If `set_renv=TRUE` it will save a hidden token named `.rtweet_token.rds` which will be used as the default evironemnt twietter token variable. 

More information about this can be found at [Obtaining and using access tokens](https://cran.r-project.org/web/packages/rtweet/vignettes/auth.html).

The function `rtweet::search_tweets` returns tweets already as a data frame.

```{r eval=FALSE}
appname <- 'Rladies_app'
api_key <-'your_api_key'
api_secret<- 'your_api_secret'

setup_twitter_oauth(api_key, api_secret, token, token_secret)

## create token named "twitter_token"
twitter_token <- create_token(
  app = appname,
  consumer_key = key,
  consumer_secret = secret)

MyTweet <- search_tweets('#MyChosenHastags',lang="en", token = twitter_token)
```
