---
title: 'Exercises - Follow Me: Introduction to social media analysis in R'
author: "Maria Prokofieva, Anna Quaglieri, Saskia Freytag"
date: "useR! July 2018"
output:
  html_document:
    theme: simplex
    toc: yes
    toc_depth: 3
  github_document:
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(icon)
library(emo)
```

For the last hour we want you to apply your new knowledge to your favourite social media platform. So pick one of the exercises and have fun!

## 1. Twitter challenge 

Compare tweets which mention Harry to tweets mentioning Meghan in the Royal `r emo::ji("crown")` Wedding time series. You can find the data in the folder `Twitter_Tutorial_data/combined_royal_time_series.csv` (you can also downloaded from [Google Drive](https://drive.google.com/file/d/1ewstbsmeenfP7Uf38R5NrMsl7tPoyoSN/view?usp=sharing)). Produce a plot that showcases your findings and post it to twitter using the hashtags \#useR2018, \#rstats and \#socialmediachallenge. Extra points for being able to upload your results trough R!

The data provided is exactly the same as the `all_words` data frame created during the tutorial (replicated tweets are removed)

```{r eval=FALSE}
library(tidyverse)
library(here)

# Load data
all_words <- read_csv(file.path(here(),"Twitter_Tutorial_data/combined_royal_time_series.csv"))
```

Here are some hints for the analysis to detect `Harry` and `Meghan` words within the tweets:

```{r eval=FALSE}
mutate(Harry = str_detect(string = text ,pattern = "harry"),
    Meghan = str_detect(string = text ,pattern = "meghan|megan|markle")) %>%
mutate(Harry_Meghan = case_when(Harry & !Meghan ~ "Harry",
                                  Meghan & !Harry ~ "Meghan",
                                  Harry & Meghan ~ "Harry_Meghan",
                                  TRUE ~ "none"))
```


* wordcloud
* sentiment analysis
* timeseries
* <https://www.tidytextmining.com/twitter.html>

Here are some hints for uploading through R:

* `twitteR::updateStatus`
* <https://blog.rladies.org/post/deployment/>




